\section{The fixed-point formulation}
\label{sec:setup}

Every standard pool operation triggers a sync, and every sync must publish one
number: the senior share rate $y$. \Cref{sec:overview:dawn-to-dusk}
showed why this is a fixed point, not an oracle read. This section makes
it precise: one equation in one unknown, then two facts about one
function.

\subsection{What we must prove}
\label{sec:setup:roadmap}

Write the senior NAV the sync must produce as $x$. We will see that a
self-consistent $x$ is exactly a zero of the \emph{error function}
\[
  E(x) \;=\; F\!\left(P_A(x / N)\right) - x,
\]
where $P_A$ values the junior collateral at a candidate rate and $F$ is
the accountant's sync map. The on-chain solver finds the largest such zero by
integer bisection, and the argument needs exactly two facts:

\begin{description}
  \item[(Monotonicity)] $E$ never rises: each step holds or falls by
    exactly one. So the values where $E \geq 0$ form an initial segment
    whose right endpoint, the crossing, is \emph{unique} even when
    several zeros tie along it, and bisection knows which way to step.
  \item[(Bracketing)] $E$ is non-negative at the bottom of the search range
    and negative at the top. This makes the crossing \emph{exist} and
    brackets it.
\end{description}

The rest of this section defines the three objects $F$, $P_A$, and $E$.
\Cref{sec:existence} proves the two facts. \Cref{sec:solver} runs the
solver. The argument rests on nothing else.

\subsection{The sync map $F$}
\label{sec:setup:F}

On each sync, the Dusk kernel calls the shared Royco accountant, whose
sync map we denote $F$. Given the
current raw NAVs of both tranches, $F$ runs the attribution and
settlement steps of \cref{sec:overview:waterfall} against the stored
checkpoint and returns the effective NAVs:
\[
  F\colon \bigl(\STraw,\ \JTraw;\ \text{checkpoint}\bigr) \longmapsto (\STeff,\ \JTeff).
\]
Two properties of $F$ matter downstream (\cref{sec:overview:waterfall}).
It conserves NAV ($\STraw + \JTraw = \STeff + \JTeff$), and it is
non-decreasing and 1-Lipschitz in $\JTraw$ (\cref{lem:F}).
Conservation holds by construction: every stored checkpoint is itself a
prior output of $F$.

In a Dusk market the senior raw NAV is exogenous to the loop: it is the
value of the senior tranche's own assets, marked independently of the
pool. Only the junior raw NAV depends on the senior rate, because the
junior's collateral is the BPT. The senior side therefore drops out, and
for one sync, with $\STraw$ and the checkpoint fixed, we read $F$ as a
function of a single variable:
\[
  F\colon \JTraw \longmapsto \STeff.
\]
$F$ returns $\STeff$ \emph{gross} of protocol fees: a fee accrues as a
separate NAV claim settled outside $F$, never netted out of $\STeff$. So
$y = \STeff/N$ is consistent only when $N$ counts the same shares the
gross NAV backs, including any minted for fees.

\subsection{The BPT valuation $P_A$}
\label{sec:setup:PA}

The junior tranche owns a fraction $f$ of a Gyro E-CLP pool whose two
legs are the senior share and a quote asset. $P_A(y)$ answers one
question: with the senior share priced at a candidate rate $y$, what is
that stake worth? The stake is the junior's first-loss collateral, so
the mark must never overstate it: coverage credited against an inflated
mark is coverage the senior cannot collect. Three ingredients keep the
mark honest: a curve frozen at solve start, a fair point on that curve,
and a cap at the total share supply.

\paragraph{The frozen curve.}
Live pool balances can be pushed around within a block, so the mark
reads them once at solve start and never re-reads them while solving.
The kernel reads the cached rate $y_0$ at that point and computes the
pool invariant $L$ from the rate-scaled balances, rounded down in favour
of the senior tranche. $L$ is then held fixed while the candidate rate
$y$ varies, which makes $P_A$ a function of $y$ alone. The monotonicity
proof relies on exactly this. The scaling and rounding details are
collected in \cref{sec:solver:obligations}.

\paragraph{Two parameterizations.}
Reading the balances once and freezing them is what resists
manipulation, and it still leaves open how the candidate rate $y$ enters
the value. Two designs answer differently. The \emph{frozen curve},
developed here, fixes the invariant $L$ and lets $y$ enter through the
price, so the mark slides along one fixed curve. \emph{Rate-scaling},
used by the reference implementation, fixes the prices and lets $y$
enter through the senior balance, rebuilding the curve at each candidate
rate from the frozen balances scaled by $y$. Both read the live balances
once and freeze them, so manipulation resistance does not distinguish
them: the per-probe recomputation under rate-scaling works from the
frozen balances, never from a fresh read. The two are different
functions of $y$, so three of the results below depend on the choice:
the value the clamp retains at rate zero, the upper bracket $V_{\max}$,
and the covered case. Each is stated in the form that holds under both,
with the frozen curve as the special case the rest of this section
and \cref{sec:existence} develop.

\paragraph{The fair point.}
Given $L$, the pool is valued at the one point on the frozen curve
consistent with the candidate price: the point whose \emph{marginal
price} (its local slope, the spot rate for an infinitesimal trade)
equals $y$. Valuing any other point would mark the pool as if it were
quoting a price the candidate rate contradicts. Write $V(y)$ for the
pool's fair value at that point, and
\[
  D(y) \;=\; V'(y),
\]
the pool's \emph{demand} for senior shares at price $y$, that is, the
senior reserve the fair point holds. The proofs need one geometric
fact, the envelope theorem of \cref{sec:existence:mono}: $V$ is
non-decreasing, with $V'(y) = D(y) \geq 0$ (a higher senior price
raises the value of the senior shares the pool holds). The structural
facts an auditor confirms per market are collected in
\cref{sec:existence:generality}.

\paragraph{The clamp.}
At low rates the frozen curve can demand more senior shares than
exist: the quote leg would notionally absorb more than the total
supply $N$, even if every holder sold into the pool. Coverage resting
on shares beyond the $N$ that exist is phantom coverage, so the demand
is capped at the supply:
\[
  \Dc(y) \;=\; \min\bigl(D(y),\ N\bigr),
  \qquad
  \widehat{V}(y) \;=\; V(0) \;+\; \int_0^y \Dc(u)\,du.
\]
The retained $V(0)$ is the pool's value at rate zero: the reserve it
still holds once the senior leg is marked to nothing. With
$\Dc \leq D = V'$ this gives $V(0) \leq \widehat{V} \leq V$ everywhere,
so the cap only ever lowers the mark, never below that rate-zero
reserve. The two values differ by exactly the phantom area,
\[
  V(y) - \widehat{V}(y)
    \;=\; \int_0^y \bigl(D(u) - N\bigr)^{+}\,du,
\]
so $\widehat{V}$ discards the phantom and keeps everything else. Under
the frozen curve the all-senior corner holds no quote, so $V(0) = 0$:
the retained term drops, $\widehat{V}$ is the bare integral
$\int_0^y \Dc$, and the gap vanishes at any rate below which demand
never exceeds $N$. Under rate-scaling, marking the senior leg to zero
leaves the quote tokens in place, so $V(0)$ is that quote leg and is
positive; dropping it would under-mark the junior by the whole quote leg
at every rate, including the healthy range where the cap is inactive. At
healthy rates the cap is inactive and $\widehat{V} = V$ wherever demand
stays under $N$; its bite is reserved for the danger zone.

\paragraph{The valuation.}
The junior tranche's pro-rata claim, rounded down in favour of the
senior tranche, is the \emph{conservative BPT valuation}:
\begin{equation}
  P_A(y) \;=\; \bigl\lfloor\, f \cdot \widehat{V}(y) \,\bigr\rfloor.
  \label{eq:PA}
\end{equation}
By the geometric fact and the clamp, $f\widehat{V}$ is non-decreasing
in $y$ and Lipschitz with constant $f N$, so the floor moves $P_A$ by
$0$ or $1$ per unit step of $x$ (\cref{sec:existence:mono}).

\paragraph{Why trading cannot lift the mark.}
Within a solve, $V$ depends only on $L$ and $y$, never on the live
pool composition. A fee-free swap conserves the pool's true invariant,
and the $L$ the solver consumes is a round-down underestimate of it,
so $L \leq L_{\mathrm{true}}$ for every reachable composition. A swap
(or a donation, which Balancer V3 ignores since it accounts
internally) can therefore move the mark only within the round-down
band, never above the true fair value.

In summary, \emph{conservative} carries three independent senses in
this document, and the valuation is built to have all three.
\begin{description}
  \item[Manipulation-bounded.] The mark reads the frozen invariant $L$
    and the fair point, not live pool balances, so trading moves it only
    within the round-down band above.
  \item[Senior-favouring.] Every rounding step (the floor in $P_A$,
    the round-down of $L$, the published rate toward senior) breaks
    ties for the protected tranche.
  \item[Capped lower bound.] The clamp $\min(D, N)$ under-marks by
    exactly the phantom area above, precisely where demand exceeds the
    shares that exist.
\end{description}
The published senior rate $y^\star$ is built on this capped
lower-bound valuation by design. \Cref{sec:existence} turns the same
cap into unconditional monotonicity.

\subsection{The fixed-point equation}
\label{sec:setup:circularity}

Chaining the definitions, $\JTraw = P_A(\STeff/N)$ and
$\STeff = F(\JTraw)$, so the senior NAV must reproduce itself:
\begin{equation}
  x \;=\; F\!\left(P_A\!\left(x / N\right)\right).
  \label{eq:fixed-point}
\end{equation}
A solution is a zero of the error function $E$
(\cref{sec:setup:roadmap}), and the published rate is
$y^\star = x^\star / N$. \Cref{sec:existence} proves the zeros of $E$ form one
contiguous block whose largest element is the published root $x^\star$
(Monotonicity), inside a range across which $E$ changes sign
(Bracketing).
