\section{The on-chain solver}
\label{sec:solver}

\Cref{thm:main} gives a unique largest root $x^\star$ in a bracket whose
endpoints straddle the sign change. This section runs the solver: integer bisection, in bounded gas. The
conditions that make the theorem apply on-chain are stated as explicit
obligations.

\subsection{Integer bisection}
\label{sec:solver:bisection}

The solver bisects $E$ on $\mathcal{B}$ at integer (WAD) precision. Each
step halves the bracket and keeps the half whose endpoints still straddle
the sign change. The bracket holds $\lvert\mathcal{B}\rvert = x_{\max}+1$
integers, so $\lceil \log_2(\lvert\mathcal{B}\rvert) \rceil$ steps
collapse it to a single integer $x^\star$, the boundary with
$E(x^\star) \geq 0 > E(x^\star + 1)$. The deployed iteration count $K$
is hardcoded per market as an upper bound on this count over every
reachable bracket ($2^K \geq x_{\max} + 1$, sized from the maximum
representable $x_{\max}$), so the collapse completes within $K$ steps
on every solve. The published rate is
$y^\star = x^\star / N$, rounded toward the senior tranche.

Bisection, not Newton, for three reasons. $F$ is non-smooth, its slope
jumping at branch boundaries (\cref{lem:F}), so a tangent-following
method has no derivative to follow, whereas bisection needs only that
$E$ be non-increasing. The iteration count $K$ is fixed at deploy time,
so gas is constant with no data-dependent exit. And the loop is a short
sweep over already-audited valuation code, with no invariant inversion
and a unique predicate boundary.

\subsection{Probe value reuse}
\label{sec:solver:reuse}

Write the loop output as $G(x) = F(P_A(x/N))$, so $E(x) = G(x) - x$. To
get the sign of $E(z)$ the solver already evaluates $G(z)$ in full --- it
prices the junior collateral at the candidate rate and runs the
waterfall --- then keeps one bit and discards the number. But that number
is not merely a test statistic. Monotonicity
(\cref{sec:existence:mono}) certifies $G(z)$ as a bracket endpoint on the
correct side of the root, usually far tighter than the midpoint rule
reaches in many steps.

\begin{lemma}[probe upgrade]
\label{lem:probe-upgrade}
Let $z$ be a probe and $v = E(z)$, so the loop output $G(z) = z + v$ is
already in hand. If $v \geq 0$ then $z \leq x^\star$ and
$G(z) \in [z,\ x^\star]$; if $v < 0$ then $z > x^\star$ and
$G(z) \in [x^\star,\ z-1]$. Either way $G(z)$ is a valid endpoint on
$z$'s side of the root, no farther from $x^\star$ than $z$.
\end{lemma}

\begin{proof}
By Monotonicity (\cref{sec:existence:mono}) the integers with $E \geq 0$
are exactly $[0, x^\star]$, so the sign of $v$ locates $z$ relative to
$x^\star$. And $G = F \circ P_A$ is non-decreasing, both factors being so
(\cref{sec:existence:mono,lem:F}). If $z \leq x^\star$: $G(z) \leq
G(x^\star) = x^\star$ and $G(z) = z + v \geq z$. If $z > x^\star$:
$G(z) \geq G(x^\star) = x^\star$ and $G(z) = z + v \leq z - 1$, since
$v \leq -1$.
\end{proof}

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
  >={Stealth[length=2.2mm]},
  font=\small,
  scale=0.62,
]
  % axes
  \draw[->] (0,0) -- (10.4,0) node[right] {$x$};
  \draw[->] (0,0) -- (0,8.8) node[above] {$G(x)$};
  % diagonal y = x
  \draw[gray] (0,0) -- (8,8) node[above right, black] {$y = x$};
  % return map G (slope < 1), crossing the diagonal at x*
  \draw[very thick, blue] (0,2) -- (9,6.05) node[right, black] {$G$};
  % root: G(x*) = x*  (2 + 0.45 x = x  =>  x = 3.636)
  \fill (3.636,3.636) circle (2.2pt);
  \draw[dashed] (3.636,3.636) -- (3.636,0) node[below] {$x^\star$};
  % right probe z (upper-endpoint case): curve point below diagonal, above x*
  \draw[dashed] (8,0) node[below] {$z$} -- (8,8);
  \fill[red] (8,5.6) circle (2.2pt);
  \draw[red,->] (8,8) -- (8,5.6) node[midway,right] {$E(z)<0$};
  \draw[red,->] (8,5.6) -- (5.6,5.6) node[midway,above] {new $\mathit{hi}=G(z)$};
  \fill[red] (5.6,5.6) circle (1.7pt);
  % left probe z' (lower-endpoint case): curve point above diagonal, below x*
  \draw[dashed] (1,0) node[below] {$z'$} -- (1,2.45);
  \fill[teal] (1,2.45) circle (2.2pt);
  \draw[teal,->] (1,1) -- (1,2.45) node[midway,left] {$E(z')>0$};
  \draw[teal,->] (1,2.45) -- (2.45,2.45) node[midway,above] {new $\mathit{lo}=G(z')$};
  \fill[teal] (2.45,2.45) circle (1.7pt);
\end{tikzpicture}
\caption{Probe value reuse, one step. The root $x^\star$ is where the
return map $G$ meets the diagonal $y = x$. A probe at $z$ right of the
root lands the curve point $(z, G(z))$ below the diagonal yet no lower
than $x^\star$ (\cref{lem:probe-upgrade}); sliding horizontally to the
diagonal makes $G(z)$ the new upper endpoint, already past the midpoint
and toward the root. A probe $z'$ left of the root gives a new lower
endpoint symmetrically. On a flat stretch of $G$ --- a covered, locally
inert market state --- the first slide lands at the root's level at once:
the $2$--$3$ probe solve of \cref{prop:reuse}.}
\label{fig:reuse}
\end{figure}

The solver applies the lemma at every step: where plain bisection moves
the endpoint to the midpoint $m$, value reuse moves it to the value the
midpoint returned, $G(m) = m + v$. Maintaining $x^\star \in [\mathit{lo},
\mathit{hi}]$ from the bracket of \cref{thm:main}:
\[
\begin{aligned}
  &(\mathit{lo},\ \mathit{hi}) \gets (0,\ x_{\max} - 1) \\
  &\textbf{while } \mathit{hi} > \mathit{lo}: \\
  &\quad m \gets \mathit{lo} + \lceil (\mathit{hi} - \mathit{lo})/2 \rceil \\
  &\quad v \gets E(m) \qquad \text{(one probe; } G(m) = m + v \text{)} \\
  &\quad \textbf{if } v \geq 0:\ \mathit{lo} \gets m + v
        \quad \textbf{else}:\ \mathit{hi} \gets m + v \\
  &\textbf{return } \mathit{lo}
\end{aligned}
\]

\begin{proposition}[value reuse is free]
\label{prop:reuse}
The loop maintains $x^\star \in [\mathit{lo}, \mathit{hi}]$, terminates in
at most $K$ probes --- the same worst case as \cref{sec:solver:bisection}
--- and returns the bit-identical $x^\star$, including the largest-integer
selection on the $f = 1$ plateau (\cref{rem:plateau}). The published rate,
the committed checkpoint, and the obligations of
\cref{sec:solver:obligations} are all unchanged.
\end{proposition}

\begin{proof}
The invariant holds initially by Bracketing
(\cref{sec:existence:sign}); each update replaces an endpoint by $G(m)$,
which \cref{lem:probe-upgrade} places between that endpoint and $x^\star$
inclusive. Progress: $\mathit{lo} < m \leq \mathit{hi}$, so the $v \geq 0$
branch gives $\mathit{lo}' = m + v \geq m > \mathit{lo}$ and the $v < 0$
branch gives $\mathit{hi}' = m + v \leq m - 1 < \mathit{hi}$ --- never
worse than moving to the midpoint, so the $\lceil \log_2 \rceil$ bound is
inherited and reuse can only beat it. At termination $\mathit{lo} =
\mathit{hi} = x^\star$. On the $f = 1$ plateau the $v \geq 0$ branch
pushes $\mathit{lo}$ upward through the block ($\mathit{lo}' = G(m) \geq
m$), so the returned point is the largest integer with $E \geq 0$, the
$x^\star$ of \cref{thm:main}. The only change from
\cref{sec:solver:bisection} is the bracket-update rule.
\end{proof}

The gain is large because the recursion is locally inert wherever the
junior buffer fully covers the senior delta
($\partial \STeff / \partial \JTraw = 0$): one value jump lands on the
root, so healthy and stressed-but-covered states --- including $f = 1$
and a binding clamp --- solve in $2$--$3$ probes. The loop is live only
where the senior holds claims on the pool leg (IL recovery, cross-claim
attribution, the yield split), and there each jump still shrinks the
overshoot by the local gain, so even deep distress converges in $\sim 20$
probes against the $\sim 64$ of width-limited bisection. Since the solve
runs on every swap, add, and remove, this is a $5$--$30\times$ cut in
solver gas on the hot path, at the cost of a single changed line and no
new assumptions.

\subsection{The search bracket and the expressible range}
\label{sec:solver:bracket}

The solver uses the \emph{conservation bracket} $\mathcal{B}$ of
\cref{thm:main} as its search domain. Its endpoints bracket $x^\star$ by
construction, so the search always returns it. Each probe
evaluates the frozen-$L$ valuation in closed form, not the pool's
invariant solver, so no probe re-triggers the E-CLP domain check. That
check runs once, when $L$ is computed at solve start from the live
balances.

The largest root $x^\star$ is the economically correct answer, but the
deployed pool can only \emph{quote} rates inside its price band. Write
$\alpha$ and $\beta$ for the lower and upper bounds on the senior rate
$y = x/N$ after the pool's configured price band has been mapped into
senior-rate units. With this convention the expressible range is
\begin{equation}
  x \;\in\; [N\alpha,\ N\beta].
\end{equation}
The symbols $\alpha$ and $\beta$ are therefore paper-level senior-rate
bounds, not necessarily the raw token0/token1 bounds stored in the pool.

The implementation must compute these senior-rate bounds from the
deployed pool configuration. That mapping depends on the actual token
ordering, the pool's price convention, and the rate-scaling convention:
if the configured price is quote-per-senior the orientation is direct,
while if it is senior-per-quote the bounds are reciprocals and swapped.
Because Balancer token ordering is determined by token addresses, the
implementation must derive this mapping from the registered pool tokens
rather than hard-coding either orientation.

After solving, the kernel checks $x^\star \in [N\alpha, N\beta]$. When it
holds, the kernel publishes $y^\star$ and operations proceed normally.
When $x^\star$ falls outside, the rate is real but unquotable --- and the
kernel does \emph{not} revert the sync. The solved root is still the honest
mark: NAV conservation holds and $P_A$ is a conservative lower bound
whatever the band (below it the valuation is the all-senior extension of
\cref{sec:solver:convergence}), so the accountant checkpoint commits at
$y^\star$ as usual. What the kernel withholds is the \emph{tradeable} rate.
An unquotable rate would have the pool price against a value it cannot
represent, so its secondary market is suspended: operations that consume a
quote --- swaps and unbalanced, single-sided liquidity --- revert, while
operations that do not --- primary senior issuance and redemption, which
touch only the senior tranche's exogenous assets, and proportional junior
add and remove, which is balance-ratio math with no price --- proceed
against the committed checkpoint. Senior protection across this state is
held by the shared accountant's coverage requirement, which gates junior
withdrawals independently of the band; the band governs only what the pool
can \emph{quote}, never whether the market can \emph{settle}. The
out-of-band condition is thus a genuine economic signal --- a senior loss
larger than the pool's band can represent --- and the response is to close
the secondary market while keeping primary issuance and redemption live,
not to freeze the market. Which operations read the published rate, and so
which the suspension must gate, is an implementation obligation
(\cref{sec:solver:freshness}).

\subsection{Computing the bracket endpoint}
\label{sec:solver:endpoint}

The upper endpoint $x_{\max} = \STraw + \lfloor f\,V_{\max}\rfloor + 1$
(\cref{thm:main}) needs one pool-derived number: a conservative upper
bound on the junior mark. Since $P_A(y) = \lfloor f\,\widehat{V}(y)\rfloor$
and $\widehat{V}$ is non-decreasing with $\widehat{V}' = \Dc = \min(D, N)$
vanishing above the band, the mark is largest at the upper band edge,
\[
  \sup_{y} \widehat{V}(y) \;=\; \widehat{V}(\beta) \;\leq\; V_{\max}.
\]
The implementation uses this tighter $\widehat{V}(\beta)$: it is the exact
supremum of the clamped valuation, whereas $V_{\max} = \sup_y V(y)$
over-marks by the area the clamp discards. The bracketing argument of
\cref{sec:existence:sign} is untouched, since
$P_A \leq \lfloor f\,\widehat{V}(\beta)\rfloor \leq \lfloor f\,V_{\max}\rfloor$
at every candidate. This subsection records how $\widehat{V}(\beta)$ is
computed; the construction is pool-specific and given here for the Gyro
E-CLP.

\paragraph{The threshold rate.}
$D(y)$, the pool's demand for senior shares (equivalently the senior
reserve at the fair point), is non-increasing in $y$: it sits at its
all-senior plateau $D(\alpha)$ below the band, falls across it, and reaches
$0$ at the all-quote corner $\beta$. The clamp $\min(D, N)$ binds exactly
where $D > N$. If $D(\alpha) \leq N$ the pool can never demand more senior
shares than exist, the clamp never binds, and $\widehat{V}(\beta) =
V_{\max}$. Otherwise there is a unique \emph{threshold rate} $y_N$ in the
band with
\[
  D(y_N) \;=\; N,
\]
the clamp binding on $[0, y_N]$ and releasing on $[y_N, \beta]$.

\paragraph{The corner value.}
Splitting $\widehat{V}(\beta) = \int_0^\beta \min(D, N)$ at $y_N$ --- the
integrand is the constant $N$ below it and $D = V'$ above it, which
telescopes --- gives the closed form of the Clamp obligation
(\cref{sec:solver:obligations}) evaluated at the corner:
\begin{equation}
  \widehat{V}(\beta)
    \;=\; \underbrace{N\,y_N}_{\text{clamped rectangle}}
        \;+\; \underbrace{\bigl(V(\beta) - V(y_N)\bigr)}_{\text{unclamped tail}}
    \;=\; V_{\max} - b_q(y_N),
  \label{eq:vhat-beta}
\end{equation}
where $b_q(y_N)$ is the quote reserve at the threshold point; the compact
right-hand form uses the fair-point identity
$V(y_N) = b_q(y_N) + y_N\,D(y_N) = b_q(y_N) + N\,y_N$. Read plainly: the
conservative corner is the all-quote value minus the quote the pool already
holds at the rate where its senior demand first meets the supply. The
discarded difference $V_{\max} - \widehat{V}(\beta)$ is exactly the
phantom-coverage gap of \cref{sec:setup:PA}, the value resting on senior
shares beyond the $N$ that exist.

\begin{figure}[!ht]
\centering
\begin{tikzpicture}[
  >={Stealth[length=2.2mm]},
  font=\small,
  scale=0.62,
]
  \def\a{2}\def\yN{4.88}\def\b{8}
  % shaded clamped area = min(D, N): rectangle [0,yN]x[0,N] + tail under D
  \fill[blue!12] (0,0) rectangle (\yN,2.6);
  \fill[blue!12] (\yN,0) -- (\yN,2.6) -- (\b,0) -- cycle;
  % axes
  \draw[->] (0,0) -- (9.6,0) node[right] {$y$};
  \draw[->] (0,0) -- (0,6.3) node[above] {$D(y)$};
  % N line
  \draw[dashed] (0,2.6) node[left] {$N$} -- (\b,2.6);
  % demand D: plateau on [0,a], linear down to 0 at b
  \draw[very thick, blue] (0,5) -- (\a,5) -- (\b,0);
  \node[blue] at (6.5,1.55) {$D$};
  \node[blue, anchor=west] at (0.15,5.4) {\footnotesize $D(\alpha)$};
  % band markers
  \draw[dashed] (\a,0) node[below] {$\alpha$} -- (\a,5);
  \draw[dashed] (\yN,0) node[below] {$y_N$} -- (\yN,2.6);
  \node[below] at (\b,0) {$\beta$};
  % piece labels
  \node[font=\footnotesize] at (2.1,1.1) {$N\,y_N$};
  \node[font=\footnotesize] at (5.75,0.62) {$V(\beta){-}V(y_N)$};
\end{tikzpicture}
\caption{The bracket endpoint $\widehat{V}(\beta) = \int_0^\beta \min(D,N)$
is the shaded area under $\min(D, N)$: a rectangle of height $N$ and width
$y_N$ where the clamp binds, plus the tail under $D$ from $y_N$ to the
all-quote corner $\beta$. The unshaded wedge between $D$ and the line $N$ on
$[0, y_N]$ --- largest near $y = 0$, where E-CLP demand grows without
bound --- is the phantom coverage the clamp discards, exactly
$V_{\max} - \widehat{V}(\beta)$.}
\label{fig:vhat-beta}
\end{figure}

\paragraph{Closed form on the E-CLP.}
Every quantity in \cref{eq:vhat-beta} is a closed-form evaluation on the
frozen curve, and the rate $y_N$ need never be materialized.
$V_{\max} = V(\beta)$ is the rate-scaled quote reserve at the all-quote
corner --- the curve's maximal balance for the quote leg (\code{maxBalances})
at the frozen invariant $L$ --- and the same corner quantity for the senior
leg is the $D(\alpha)$ the guard above compares against $N$. The threshold's
conjugate reserve $b_q(y_N)$ comes straight from the curve's
reserve-given-reserve map: fixing the senior real reserve at $N$ returns the
quote reserve at the unique curve point where senior demand meets the supply
(\code{calcYGivenX} for a senior token0, \code{calcXGivenY} for token1) --- a
closed-form ellipse inversion, no iteration. The endpoint is then
$\widehat{V}(\beta) = V_{\max} - b_q(y_N)$; the rate $y_N$ is just the spot
price at that same point, needed only if the in-band check
$y_N \in [\alpha, \beta]$ is performed, never for the value. Here $N$ enters
in the pool's rate-scaled balance units, the senior leg scaled at the frozen
$y_0$. All evaluations run on the frozen curve the probes use
(\cref{sec:setup:PA}), so none re-triggers the pool's domain check.

\paragraph{Rounding.}
$\widehat{V}(\beta)$ is the one quantity rounded \emph{up}. Every other
rounding favours the senior tranche by rounding down (the floor in $P_A$,
the invariant $L$, the published rate); an endpoint instead must certify a
sign, so it may not underestimate the mark it bounds. Rounding
$\widehat{V}(\beta)$ up --- equivalently, one wei added to a rounded-down
library output --- keeps $x_{\max}$ a strict over-estimate and the
bracketing of \cref{thm:main} intact.

\subsection{Why the solve always converges}
\label{sec:solver:convergence}

\Cref{thm:main} is a statement about the function $E$. For it to govern
the on-chain loop, three implementation invariants must hold. Each is
cheap and is listed as an obligation in \cref{sec:solver:obligations}.

\begin{description}
  \item[Frozen inputs.] Every input to $E$ ($\STraw$, $N$, $f$, the
    invariant $L$, the cached rate $y_0$, and the checkpoint) is read
    once at solve start and never re-read. Bisection compares $E$ at
    different probes and assumes one fixed function. Any external reads
    inside $F$ (the yield-model view, the block timestamp) are constant
    across the bisection, since it runs in one block against a frozen
    checkpoint, so no probe sees a different function.
  \item[Live supply.] $N \geq 1$. The map divides by $N$, so the supply
    must be positive. This is a \emph{Dusk obligation}, not a property
    inherited from the shared tranche. The Dawn senior tranche mints
    shares only on deposit and burns them on redemption, seeds nothing at
    market creation, and applies no virtual-share offset in its
    conversion (at zero supply it converts one-to-one), so its supply can
    fall back to zero. A Dusk market must therefore pin $N \geq 1$ for the
    life of the market by construction, for instance a non-redeemable
    minimum senior position seeded at creation or a virtual-share offset
    in the senior conversion, so the division is always defined. The
    same floor is what discharges the $N \geq 1$ hypothesis of
    \cref{thm:main}.
  \item[Total $E$.] Every probe returns a value rather than reverting.
    $E$ has two parts. $P_A$ is the closed-form frozen-curve valuation,
    total on $\mathcal{B}$ by construction: below the band it is the
    all-senior line, above it the constant $V_{\max}$, and the E-CLP
    domain check runs only once, at $L$-computation
    (\S\ref{sec:solver:bracket}). $F$ reverts only on a checkpoint that
    violates NAV conservation, and every stored checkpoint, the genesis
    checkpoint included, conserves by construction
    (\cref{sec:overview:waterfall}). Its one external read, the
    yield-model view, must be a non-reverting view function (an
    obligation below). So on the reachable state space $E$
    is defined at every probe in $\mathcal{B}$.
\end{description}

Under these three invariants, the solve terminates in exactly $K$ steps
and returns the largest root $x^\star$. The only remaining reverts are external to
the solver: a paused market, a stale or reverting price oracle, or the
surrounding pool operation hitting its own Balancer limits. None of these
is a failure of the solve, and in each case the cached rate is left
untouched. Two guarantees follow, and only these two: the failed
operation reverts before it can \emph{consume} a stale rate, and a
failed sync never \emph{overwrites} the cache. Ordinary view reads
(\code{getRate}) still return the last published rate: staleness is
prevented from propagating through an operation, not from being read.

\subsection{Iteration count and rounding}
\label{sec:solver:rounding}

Two policy choices fix the solver's behaviour:
\begin{description}
  \item[Iteration count] is the $K$ of \cref{sec:solver:bisection},
    hardcoded per market to cover the largest reachable bracket,
    $2^K \geq x_{\max} + 1$. Each step of $E$ lies in $\{-1, 0\}$
    (\cref{sec:existence:mono}), so $K$ halvings collapse every
    reachable bracket to the single integer boundary $x^\star$. No
    residual or iteration-count check is needed.
  \item[Rounding] sends the published $y^\star = x^\star/N$ toward the
    senior tranche ($x^\star$ itself is an exact integer,
    \cref{sec:existence:mono}). Together with the
    floor inside $P_A$ (\cref{eq:PA}) and the round-down of the
    invariant, every rounding step favours the protected tranche.
\end{description}

\subsection{Implementation obligations}
\label{sec:solver:obligations}

The correctness argument rests on the following, each verifiable per
market. The first group makes $E$ the right function, the second makes
the solve converge, the third keeps every step conservative.

\begin{description}
  \item[Senior independence.] The senior raw NAV is marked from sources
    that do not read the pool (its BPT value, its spot price, or the
    published rate), so the loop has exactly one fixed-point variable.
  \item[Valuation wiring.] The senior leg is lifted to WAD by its
    decimal factor $10^{18 - d_s}$ ($d_s$ its native decimals) and the
    published senior rate. The quote leg is lifted by $10^{18 - d_q}$
    and its rate $q$.
  \item[Frozen curve.] $L$ is computed once per solve from the balances
    scaled at $y_0$, rounded down (the underestimate), and held fixed across the
    bisection. The bracket endpoint is the clamped corner
    $\widehat{V}(\beta) \leq V_{\max}$ of \cref{sec:solver:endpoint},
    computed from this same frozen curve and rounded up.
  \item[Clamp.] The valuation uses the integral form
    $\widehat{V}(y) = \int_0^y \min(D, N)$ (\cref{sec:setup:PA}), with $N$
    read at solve start. In closed form this is $N y$ below the rate
    where demand falls to $N$, and $V$ shifted by a constant above it
    (the split is unique when demand is monotone, as for the Gyro
    E-CLP). Capping the share count inside the point value,
    $b_q + y\min(D,N)$, is a different function that is not $N$-Lipschitz
    and can break monotonicity.
  \item[Frozen inputs, live supply, total $E$.] As in
    \cref{sec:solver:convergence}: read once, $N \geq 1$, conserving
    checkpoint.
  \item[Total probes.] The closed-form valuation is defined for every
    $x \in \mathcal{B}$, including the band extensions below $\alpha$
    (all senior) and above $\beta$ (all quote), and the yield-model view
    is a non-reverting view function. $P_A$ is evaluated at full
    precision in $x$, never through a quantized intermediate rate, so a
    unit step of $x$ moves $f\widehat{V}$ by at most $f$, the bound
    Stage 1 of \cref{sec:existence:mono} assumes. A quantized rate
    batches many $x$-steps into one jump of the mark and breaks the
    step bound.
  \item[Non-negative mark.] $\STraw \geq 0$, the hypothesis
    \cref{thm:main} consumes at the lower endpoint
    (\cref{sec:existence:sign}). A raw NAV marks deposited assets, so a
    conforming quoter cannot report a negative value. One that can must
    revert instead of returning it.
  \item[Conservative rounding.] Senior-favouring at every step: the
    invariant down, the valuation floor, and the published rate toward
    senior.
\end{description}

\subsection{Rate-freshness obligations}
\label{sec:solver:freshness}

The solver publishes $y^\star$, and the surrounding pool must consume
it freshly. These obligations are on the wiring between hook, kernel,
and pool rather than on the solve, and are listed for the implementer.

\begin{description}
  \item[Sync coverage.] The hook registers all three before-operation
    callbacks (before-swap, before-add, and before-remove), so
    every standard operation triggers a sync. Recovery-mode removes are
    the one carve-out, listed below.
  \item[Reload ordering.] The kernel syncs inside the matching before
    branch, and Balancer reloads balances and rates for that operation only
    after the hook returns, so the operation executes against the freshly
    published rate. The reload reads the Vault's own internal balances, so
    the hook must publish through a Vault entrypoint, since a raw token
    transfer into the pool is not seen by the reload.
  \item[Non-reverting view.] \code{getRate} returns the cached $y^\star$
    and must not revert merely because the rate looks stale.
  \item[Failure semantics.] A failed sync reverts the operation and does
    not overwrite the cache, and ordinary view reads still return the
    last published rate (\cref{sec:solver:convergence}).
  \item[Unquotable rate.] When the solved root falls outside the
    expressible range $[N\alpha, N\beta]$ (\cref{sec:solver:bracket}), the
    sync still commits the checkpoint at $y^\star$; the kernel withholds
    $y^\star$ as a tradeable rate and gates the pool's secondary market.
    Operations that consume a quote (swaps, unbalanced liquidity) revert;
    primary senior issuance and redemption and proportional junior
    add and remove proceed. The implementer must confirm which Balancer
    paths read the published rate --- in particular that proportional
    removes settle on raw balances without it --- and wire the suspension
    to match. The last quotable rate is left cached for view reads.
  \item[Recovery mode.] Recovery-mode removes are a separate path, not
    bound by this contract.
\end{description}
